Effects of the body force on the evacuation dynamics

### 2019-12-19 paper.tex
agregue mas texto en la parte de resultados (bottleneck)

Notice that the faster-is-slower (FIS) effect and the faster-is-faster (FIF) effect are both dependent on the value of $k$. If $k$ is high enough, the FIF effect does not show for the explored desired velocity values ($v_d \leq 10$~m/s).\\

@@

>>>>

The Faster-is-Faster (FIF) is the phenomenon in which under certain conditions, increasing the desired velocity yields to a reduction of the evacuation time. While the Faster-is-Faster is the opposite (the higher $v_d$ the lower the evacuation time).  Notice that the presence of the faster-is-faster (FIF) effect and the faster-is-slower are dependent on the value of $k$. In Fig.~\ref{vd_vs_te} we can see that $k=1.2$~E5 only exhibits FIS effect for $v_d>$2~m/s. $k=1.2$~E6 only shows FIF effect and the explored values of $k$ that satisfy $k \leq 6$~E4 exhibit both the FIS and the FIF effect. \\

@@

Network analysis is a set of techniques that characterize the structures in a given graph. We defined the graph of contacts among individuals. In this graph, each node represents a pedestrian and the link between a pair of nodes is settled if this pair of pedestrians are in physical contact ($i.e.$ $r_{ij}<d_{ij}$).\\

Fig.~\ref{degree_te}
